In the rapidly evolving landscape of artificial intelligence, diffusion models have emerged as a groundbreaking approach, offering transformative capabilities across a wide array of applications. These models, through a process of iterative refinement, have unlocked unprecedented potential in creative and analytical tasks alike. Among their most notable applications are Text to Image generation, where models synthesize visually compelling images from descriptive text, blending creativity with precision to bridge the gap between textual concepts and their visual representations. In Image to Image translation, they adeptly modify or transform one image into another style or context, showcasing their versatility in reimagining visual content. Image editing with diffusion models goes a step further, allowing for nuanced adjustments and enhancements that redefine the boundaries of digital artistry. In the realm of Video, these models extend their prowess to dynamic sequences, enabling the generation and modification of video content with an eye for detail and continuity. The exploration into 3D brings a spatial dimension to their capabilities, where diffusion models generate and manipulate three-dimensional objects and environments, opening new frontiers in virtual and augmented reality. Lastly, their application in Document Layout emphasizes their utility beyond the visual arts, automating the design of document structures in a way that balances aesthetics with information delivery. This diverse spectrum of applications not only highlights the versatility of diffusion models but also sets the stage for their future developments, promising to redefine the intersection of technology and creativity.

\subsection{Text to Image}
\input{sections/applications/t2i}

\subsection{Image To Image}
\input{sections/applications/i2i}

\subsection{Image editing}
\input{sections/applications/image_editing}

\subsection{Video}
\input{sections/applications/video_editing}

\subsection{3D}
\input{sections/applications/3d}

\subsection{Document Layout}
\input{sections/applications/doc}
